\bf On semidefinite-representable sets over valuation fields

### 2025-05-16 article/paper_padic_spec.tex
commit by Simone

In this section we present an algorithm for solving \eqref{LP} which starts by
eliminating the equality constraint defined by $D$ and $e$ by operating a substitution.
Then the algorithm reduces the matrix $A$ to Smith Normal Form, thus reducing a general
linear program to a diagonal linear program. The original problem is then easily solved
by looking at valuations of input data of the reduced problem.

@@

We formalize the algorithm described previously in \Cref{algo_LP}:

>>>>

In this section we present an algorithm for solving Problem \eqref{LP}.
The algorithm starts by eliminating the equality constraint defined by $D$ and $e$
by variable substitution. Then the matrix $A$ is replaced by its Smith Normal Form,
and the general linear program is consequently reduced to a diagonal linear program.
The original \eqref{LP} is then easily solved by looking at valuations of input data
in the reduced problem.

We first give a formal description of our algorithm and then prove its correctness:

@@
